|

### 2019-08-26 paper.Rmd
additions to short technical note'

---
title: |
  A slice tour
type: Short Technical Note
author:
  - name: Ursula Laa
    affil: a, b
    email: ursula.laa@monash.edu
  - name: Dianne Cook
    affil: b
    email: dicook@monash.edu
affiliation:
  - num: a
    address: |
      School of Physics and Astronomy, Monash University
  - num: b
    address: |
      Department of Econometrics and Business Statistics, Monash University
bibliography: biblio.bib
abstract: |
  Projections and sectioning are complementary methods for the visualisation of
  high-dimensional data. In this note we describe slicing in the orthogonal
  space of projections obtained when running a tour, thus presenting the viewer
  with an interpolated sequence of projected sections. The method has been
  implemented in R as an extension to the tourr package, and can be used to
  explore concave structures in multivariate distributions.
keywords: |
  data visualisation; grand tour; sectioning
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
output: rticles::tf_article
---

@@

@@

@@

# Example

>>>>

---
title: |
  A slice tour for finding hollowness in high-dimensional data
type: Short Technical Note
author:
  - name: Ursula Laa
    affil: a, b
    email: ursula.laa@monash.edu
  - name: Dianne Cook
    affil: b
    email: dicook@monash.edu
affiliation:
  - num: a
    address: |
      School of Physics and Astronomy, Monash University
  - num: b
    address: |
      Department of Econometrics and Business Statistics, Monash University
bibliography: biblio.bib
abstract: |
  Projections and sectioning are complementary methods for the visualisation of
  high-dimensional data. In this note we describe slicing in the orthogonal
  space of projections obtained when running a tour, thus presenting the viewer
  with an interpolated sequence of projected sections. The method has been
  implemented in R as an extension to the tourr package, and can be used to
  explore concave structures in multivariate distributions.
keywords: |
  data visualisation; grand tour; sectioning
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
output: rticles::tf_article
---

@@

### Distance from the origin

@@

XXX Example 2x2, row 1-col 1 has a slice projection  of a solid 4D spehere, row 1-col 2 has a slice projectionof a hollow 4D sphere; row 2-col 1 has a slice projection of a  solid 4D cube, row 1-col 2 has a slice projection of a hollow 4D cube

### Slice thickness

@@

XXX R code

# Examples

XXX choose 6
